A Control Strategy for a Tethered Follower Robot for Pulmonary Rehabilitation

### 2020-05-12 alpibot.tex
Ajustes varios para enviar a la revista.

% The paper headers
\markboth{IEEE Latin American Transactions}%
{Bianchi \MakeLowercase{\textit{et al.}} Controller Design for a Tethered Follower Robot for Pulmonary Rehabilitation}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
COPD, PR, SAR, IoRT, tethered, leader-follower
\end{IEEEkeywords}

@@

\IEEEPARstart{C}{hronic} Obstructive Pulmonary Disease (COPD) is an umbrella term that describes several pulmonary affections.  They are characterized as a slowly progressive condition marked by airflow limitation, being cigarette smoking the main etiologic factor~\cite{MacNee2005}. This pathology presents an eskeletomuscular atrophy~\cite{Kocsis2016,Wu2012}. In order to carve these after effects a Pulmonary Rehabilitation procedure is a viable treatment for patients.  During this rehabilitation, patients undergo controlled walking activities and physical exercises under the supervision of a physical therapist.   Patients present a severe low oxygen saturation illness and they require effective oxygen supply, particularly when performing physical activity~\cite{Celli2014}.  Hence, patients require to carry with them an oxygen tank for the oxygenotherapy assistance.  However, their own condition prevent them with the ability to precisely carry the often bulky external tank.  This situation entails to find a pragmatic solution to avoid an additional physical therapist to carry the oxygen tank.  This scenario may be aggravated by the fact that this procedure is performed on a rehabilitation gym that could be potentially crowded with several patients, physiologist and physical therapists.

@@

Regarding metrics, three are proposed to evaluate the performance.  They are:

@@

A tracked marker was placed on each side of the robot (on top of each thread reel). The human leader used his hand to grab the tip at which the two tethers were tied together. A third marker was placed in his hand, using a glove. The lemniscate of Gerono, used in the simulation, was marked on the floor, and the human leader tried to move his hand following this shape as close as possible, with stable speed.  The shape was marked according to the shape described in Equation~\ref{eq:lemniscata}, using $a = 2$ [m].

@@

\begin{figure}[h!]
\centering
\includegraphics[width=8cm]{images/capture.png}
\caption{Hardware prototype on the motion capture system and a testing subject holding the threads.  The lemniscate of gerone was marked on the floor.  The subject follows this track on the performed experiments.}
\label{fig:distance_sim}
\end{figure}

@@

\begin{figure} 
    \centering
  \subfloat[ \label{1a}]{%
       \includegraphics[width=0.49\linewidth]{images/simulation_follow-thread.eps}}
    \hspace*{-1.5em}
  \subfloat[ \label{1b}]{%
        \includegraphics[width=0.49\linewidth]{images/simulation_rotate-go.eps}}
    \\
    \vspace*{-1.5em}
  \subfloat[ \label{1c}]{%
        \includegraphics[width=0.49\linewidth]{images/simulation_speed_profile_follow-thread.eps}}
    \hspace*{-1.5em}
  \subfloat[ \label{1d}]{%
        \includegraphics[width=0.49\linewidth]{images/simulation_speed_profile_rotate-go.eps}}
    \\
    \vspace*{-2.5em}
  \subfloat[ \label{1e}]{%
        \includegraphics[width=0.99\linewidth]{images/ft_vs_rg_dist.eps}}
  \caption{Simulation Results: Trajectories of the leader and follower for Follow the thread (a) and Rotate and go (b) . 
        Speed profiles of the leader and follower for Follow the thread (c) and Rotate and go (d). 
        (e) Separation distance between robot and leader for both strategies.}
  \label{fig:simulationresults} 
\end{figure}

@@

\begin{figure} 
    \centering
  \subfloat[ \label{1a}]{%
       \includegraphics[width=0.49\linewidth]{images/capture_follow-turn.eps}}
    \hspace*{-1.5em}
  \subfloat[ \label{1b}]{%
        \includegraphics[width=0.49\linewidth]{images/capture_rotate-go.eps}}
    \\
    \vspace*{-1.5em}
  \subfloat[ \label{1c}]{%
        \includegraphics[width=0.49\linewidth]{images/capture_speed_profile_follow-thread.eps}}
    \hspace*{-1.5em}
  \subfloat[ \label{1d}]{%
        \includegraphics[width=0.49\linewidth]{images/capture_speed_profile_rotate-go.eps}}
    \\
    \vspace*{-2.5em}
  \subfloat[ \label{1e}]{%
        \includegraphics[width=0.99\linewidth]{images/cap_ft_vs_rg_dist.eps}}
  \caption{Experimentation Results: Trajectories of the leader and follower for Follow the thread (a) and Rotate and go (b). 
        Speed profiles of the leader and follower for Follow the thread (c) and Rotate and go (d). 
        (e) Separation distance between robot and leader for both strategies [m].}
  \label{fig:realworldresults} 
\end{figure}

@@

From the practical experiments, it is verified that the both algorithms gave reasonable following performance in the task of following the leader along a lemniscate-shaped trajectory. This reasonable following behaviour is accomplished with a simple mechanism, a characteristic that significantly keep the price of the device low, putting it within reach of many medical institutions.

>>>>

% The paper headers
\markboth{IEEE Transactions on Neural Systems and Rehabilitation Engineering}%
{Bianchi \MakeLowercase{\textit{et al.}} A Control Strategy for a Tethered Follower Robot
for Pulmonary Rehabilitation}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
COPD, PR, SAR, IoRT, tethered
\end{IEEEkeywords}

@@

\IEEEPARstart{C}{hronic} Obstructive Pulmonary Disease (COPD) is an umbrella term that describes several pulmonary affections.  They are characterized as a slowly progressive condition marked by airflow limitation, being cigarette smoking the main etiologic factor~\cite{MacNee2005}. This pathology presents an eskeletomuscular atrophy~\cite{Kocsis2016,Wu2012}. In order to carve these after effects a Pulmonary Rehabilitation procedure is a viable treatment for patients.  During this rehabilitation, patients undergo controlled walking activities and physical exercises under the supervision of a physical therapist.   Patients present a severe low oxygen saturation illness and they require effective oxygen supply, particularly when performing physical activity~\cite{Celli2014}.  Hence, patients require to carry with them an oxygen tank for the oxygenotherapy assistance.  However, their own condition prevent them with the ability to precisely carry the often bulky external tank.  This situation entails to find a pragmatic solution to avoid an additional physical therapist to carry the oxygen tank.  This scenario may be aggravated by the fact that this procedure is performed on a rehabilitation gym that could be potentially crowded with several patients, physiologists and physical therapists.

@@

Regarding metrics, four are proposed to evaluate the performance.  They are:

@@

As shown in Figure~\ref{fig:capturesystem}, a tracking marker was placed on each side of the robot (on top of each thread reel). The human leader used his hand to grab the tip at which the two tethers were tied together. A third marker was placed in his hand, using a glove. The lemniscate of Gerono, used in the simulation, was marked on the floor, and the human leader tried to move his hand following this shape as close as possible, with stable speed.  The shape was marked according to the shape described in Equation~\ref{eq:lemniscata}, using $a = 2$ [m].

@@

\begin{figure}[h!]
\centering
\includegraphics[width=8cm]{images/capture.png}
\caption{Hardware prototype on the motion capture system and a testing subject holding the threads.  The lemniscate of gerone was marked on the floor.  The subject follows this track on the performed experiments.}
\label{fig:capturesystem}
\end{figure}

@@

\begin{figure} 
    \centering
  \subfloat[ \label{sr1a}]{%
       \includegraphics[width=0.49\linewidth]{images/simulation_follow-thread.eps}}
    \hspace*{-1.5em}
  \subfloat[ \label{sr1b}]{%
        \includegraphics[width=0.49\linewidth]{images/simulation_rotate-go.eps}}
    \\
    \vspace*{-1.1em}
  \subfloat[ \label{sr1c}]{%
        \includegraphics[width=0.49\linewidth]{images/simulation_speed_profile_follow-thread.eps}}
    \hspace*{-1.5em}
  \subfloat[ \label{sr1d}]{%
        \includegraphics[width=0.49\linewidth]{images/simulation_speed_profile_rotate-go.eps}}
    \\
    \vspace*{-2.5em}
  \subfloat[ \label{sr1e}]{%
        \includegraphics[width=0.99\linewidth]{images/ft_vs_rg_dist.eps}}
  \caption{Simulation Results: Trajectories of the leader and follower for Follow the thread (a) and Rotate and go (b) . 
        Speed profiles of the leader and follower for Follow the thread (c) and Rotate and go (d). 
        (e) Separation distance between robot and leader for both strategies.}
  \label{fig:simulationresults} 
\end{figure}

@@

\begin{figure} 
    \centering
  \subfloat[ \label{rw1a}]{%
       \includegraphics[width=0.49\linewidth]{images/capture_follow-turn.eps}}
    \hspace*{-1.5em}
  \subfloat[ \label{rw1b}]{%
        \includegraphics[width=0.49\linewidth]{images/capture_rotate-go.eps}}
    \\
    \vspace*{-1.1em}
  \subfloat[ \label{rw1c}]{%
        \includegraphics[width=0.49\linewidth]{images/capture_speed_profile_follow-thread.eps}}
    \hspace*{-1.5em}
  \subfloat[ \label{rw1d}]{%
        \includegraphics[width=0.49\linewidth]{images/capture_speed_profile_rotate-go.eps}}
    \\
    \vspace*{-2.5em}
  \subfloat[ \label{rw1e}]{%
        \includegraphics[width=0.99\linewidth]{images/cap_ft_vs_rg_dist.eps}}
  \caption{Experimentation Results: Trajectories of the leader and follower for Follow the thread (a) and Rotate and go (b). 
        Speed profiles of the leader and follower for Follow the thread (c) and Rotate and go (d). 
        (e) Separation distance between robot and leader for both strategies [m].}
  \label{fig:realworldresults} 
\end{figure}

@@

From the practical experiments, it is verified that both algorithms gave reasonable following performance in the task of following the leader along a lemniscate-shaped trajectory. This reasonable following behaviour is accomplished with a simple mechanism, a characteristic that significantly keep the price of the device low, putting it within reach of many medical institutions.
